### 2022-09-19 main/chapter_2ljets.tex
fix experiment chapter ref

A muon, for example, will tend to have its momentum measured more precisely
than a jet of similar energy.
But there are exceptions, and exceptions to the exceptions.
One exception, as discussed in Chapter~\ref{chapter:experiment}, is if the muon
is hard enough that its curvature through \atlas' magnetic fields is
imprecisely reconstructed.
A further exception to that rule can occur, however, if the jet originates from a
$b$ quark, such that the weak decays of its hadrons tend to lose momentum in
neutrinos or soft muons that are not reconstructed.

>>>>

A muon, for example, will tend to have its momentum measured more precisely
than a jet of similar energy.
But there are exceptions, and exceptions to the exceptions.
One exception, as discussed in Chapter~\ref{chapter:context}, is if the muon
is hard enough that its curvature through \atlas' magnetic fields is
imprecisely reconstructed.
A further exception to that rule can occur, however, if the jet originates from a
$b$ quark, such that the weak decays of its hadrons tend to lose momentum in
neutrinos or soft muons that are not reconstructed.
